Constructing Quotient Inductive-Inductive Types

### 2018-10-29 paper.tex
Revision note

Second, the focus of the current work differs. Cartmell's main result
was the establishment of contextual categories as classifying
categories of GATs. In contrast, we do not discuss classifying
categories\footnote{This could be included in future work.}. Instead,
we present more constructions involving algebras; these include an
explicit initial algebra construction and the CwF model, which yields
a small internal type theory of algebras for each signature, and which
in particular allows us to exactly compute eliminators and
homomorphisms as types in the meta type theory.

>>>>

Second, the focus of the current work differs. Cartmell's main result
was the establishment of contextual categories as classifying
categories of GATs. In contrast, we do not discuss classifying
categories\footnote{This could be included in future work.}. Instead,
we present more constructions involving algebras; these include an
explicit initial algebra construction and the CwF model, which yields
a small internal type theory of algebras for each signature, and which
in particular allows us to exactly compute eliminators and
homomorphisms as types in the meta type theory.\footnote{This is
demoed in \cite{kaposi_et_al:LIPIcs:2018:9190}, by a Haskell program which
takes a signature as input, type checks it, then outputs the
corresponding induction methods and eliminators as an Agda file.}
